Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-05-10 VegOzone.tex
Fix typo in table
Include gamma(0.5) value in table
Fix labeling of critical levels

\begin{table}[t]
  \caption{Bespoke light parameterizations. MM refers to mapping manual \citep{GCB:Mills2011,ICP:MappingManual2017}.}
  \label{tab:sensitivity_tests_light}
  \begin{tabular}{llr}
    \tophline
    Species & type & $\alpha$\\
    \middlehline
    \multirow{3}{*}{Deciduous tree} & MM & 0.004 \\
    & PPFD0.8 & 0.005\\
    & PPFD1.2 & 0.004\\
    \middlehline
    \multirow{3}{*}{Coniferous tree} & MM & 0.006 \\
    & PPFD0.8 & 0.008  \\
    & PPFD1.2 & 0.005  \\
    \middlehline
    \multirow{3}{*}{Perennial grassland} & MM & 0.011\\
    & PPFD0.8 & 0.014 \\
    & PPFD1.2 & 0.009 \\
    \bottomhline
    \end{tabular}
\end{table}

@@

We have modeled $\mathrm{POD_y}$ with a flux threshold $y=1\,\unit{nmol\,m^{-2}\,s^{-1}}$ per projected leaf area (PLA) for three natural/semi-natural vegetation types, deciduous trees, coniferous trees, and perennial grassland using both MM parameterizations and a variety of bespoke response function in $f_\mathrm{T}$ and $f_\mathrm{light}$, and localized GS (described in detail in Section~\ref{subsec:do3se_parameters}). The results are shown in Fig.~\ref{fig:pody_rel}. For comparison, critical levels for a $4\,\unit{\%}$ (silver birch), $2\,\unit{\%}$ (Norway spruce) \citep{ICP:MappingManual2017}, and $10\,\unit{\%}$ (perennial grassland, above ground) \citep{ESPR:Hayes2021} reduction in biomass are shown as horizontal dashed lines. Different years are color coded as previously. Simulations with MM GS, canopy, and leaf parameters are indicated with squared markers, bespoke GS with circles. The annotation $\pm$ refers to bespoke light response function threshold ($+\rightarrow\mathrm{PPFD1.2}$, $-\rightarrow\mathrm{PPFD0.8}$), while bespoke temperature response functions are indicated by categories on the x-axis. Closed/open symbols represent SWP sensitivity switched off/on in the model.

>>>>

\begin{table}[t]
  \caption{Bespoke light parameterizations. MM refers to mapping manual \citep{GCB:Mills2011,ICP:MappingManual2017}.}
  \label{tab:sensitivity_tests_light}
  \begin{tabular}{llcr}
    \tophline
    Species & type & $\alpha$ & $\gamma(0.5)$\\
    \middlehline
    \multirow{3}{*}{Deciduous tree} & MM & 0.004 & 165.035\\
    & PPFD0.8 & 0.005 & 132.028\\
    & PPFD1.2 & 0.003 & 198.042\\
    \middlehline
    \multirow{3}{*}{Coniferous tree} & MM & 0.006 & 115.525\\
    & PPFD0.8 & 0.008 & 92.420\\
    & PPFD1.2 & 0.005 & 138.629\\
    \middlehline
    \multirow{3}{*}{Perennial grassland} & MM & 0.011 & 63.013\\
    & PPFD0.8 & 0.014 & 50.411\\
    & PPFD1.2 & 0.009 & 75.616\\
    \bottomhline
    \end{tabular}
\end{table}

@@

We have modeled $\mathrm{POD_y}$ with a flux threshold $y=1\,\unit{nmol\,m^{-2}\,s^{-1}}$ per projected leaf area (PLA) for three natural/semi-natural vegetation types, deciduous trees, coniferous trees, and perennial grassland using both MM parameterizations and a variety of bespoke response function in $f_\mathrm{T}$ and $f_\mathrm{light}$, and localized GS (described in detail in Section~\ref{subsec:do3se_parameters}). The results are shown in Fig.~\ref{fig:pody_rel}. For comparison, critical levels for a $4\,\unit{\%}$ (deciduous), $2\,\unit{\%}$ (coniferous) \citep[refer to silver birch and Norway spruce in][]{ICP:MappingManual2017}, and $10\,\unit{\%}$ (perennial grassland, above ground) \citep{ESPR:Hayes2021} reduction in biomass are shown as horizontal dashed lines. Different years are color coded as previously. Simulations with MM GS, canopy, and leaf parameters are indicated with squared markers, bespoke GS with circles. The annotation $\pm$ refers to bespoke light response function threshold ($+\rightarrow\mathrm{PPFD1.2}$, $-\rightarrow\mathrm{PPFD0.8}$), while bespoke temperature response functions are indicated by categories on the x-axis. Closed/open symbols represent SWP sensitivity switched off/on in the model.
